---
title: "Statistical Supplement"
output: 
  pdf_document: 
    highlight: zenburn
    number_sections: yes
    toc: yes
editor_options: 
  chunk_output_type: inline
---

Stats for paper on AMRO eggshell thickness with Amelia and Philina

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R details and packages used
  * File creation date: `r Sys.Date()`
  * `r R.version.string`
  * `lme4` package version: `r packageVersion("lme4")`
  * `MuMIn` package version: `r packageVersion("MuMIn")`
  * 'lmerTest' package version: `r packageVersion("lmerTest")` #this package gives some test stats when running lmer models
  * 'tidyverse' package version: `r packageVersion("tidyverse")`
  * 'arm' package version: `r packageVersion("arm")`
  * 'emmeans' package version: `r packageVersion("emmeans")`
  * 'sjPlot' package version: `r packageVersion("sjPlot")`
  * 'sjstats' package version: `r packageVersion("sjstats")`
  * 'car' package version: `r packageVersion("car")`
  * 'psych' package version: `r packageVersion("psych")`
  * 'rsq' package version: `r packageVersion("rsq")`
  * 'ridge' package version: `r packageVersion("ridge")`
  * 'AICcmodavg' package version: `r packageVersion("AICcmodavg")`
  * 'summarytools' package version: `r packageVersion("summarytools")`

        
# Load packages
```{r}
library(lme4) #genlin mixed models
library(MuMIn) #model evaluation and selection
library(lmerTest) #adss tests and P to lmer
library(tidyverse) #ggplot2, dpolyr and the rest, all at once
library(arm) #Gelman's functions
library(emmeans) #used to be lsmeans
library(sjPlot) #diagnostic and other data viz plots;  gives a warning that you can ignore as we do not use the TMB package
library(sjstats) #lots of convenient functions
library(car) #lots of corrs and regression stats
library(psych) #effect size sytays, corr matrices
library(rsq) #various functions to calc R^2
library(ridge) #ridge regressions
library(AICcmodavg) #some useful model averaging functions
library(summarytools) #some basic functions for summarizing data
```

# 
```{r}
(z=2+2*8)
```

